% 参考文献
% 参考文献数据库文件：data/ref/references.bib
% 请将以下示例参考文献添加到 references.bib 文件中

\begin{thebibliography}{99}
    \setlength{\itemsep}{-2pt}
    \setlength{\baselineskip}{20pt}
    
    \bibitem{esteva2017dermatologist}
    Esteva A, Kuprel B, Novoa R A, et al. Dermatologist-level classification of skin cancer with deep neural networks[J]. Nature, 2017, 542(7639): 115-118.
    
    \bibitem{grigorescu2020survey}
    Grigorescu S, Trasnea B, Cocias T, et al. A survey of deep learning techniques for autonomous driving[J]. Journal of Field Robotics, 2020, 37(3): 362-386.
    
    \bibitem{lowe2004distinctive}
    Lowe D G. Distinctive image features from scale-invariant keypoints[J]. International Journal of Computer Vision, 2004, 60(2): 91-110.
    
    \bibitem{dalal2005histograms}
    Dalal N, Triggs B. Histograms of oriented gradients for human detection[C]// Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2005: 886-893.
    
    \bibitem{krizhevsky2012imagenet}
    Krizhevsky A, Sutskever I, Hinton G E. Imagenet classification with deep convolutional neural networks[J]. Advances in Neural Information Processing Systems, 2012, 25: 1097-1105.
    
    \bibitem{simonyan2014very}
    Simonyan K, Zisserman A. Very deep convolutional networks for large-scale image recognition[J]. arXiv preprint arXiv:1409.1556, 2014.
    
    \bibitem{szegedy2015going}
    Szegedy C, Liu W, Jia Y, et al. Going deeper with convolutions[C]// Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2015: 1-9.
    
    \bibitem{he2016deep}
    He K, Zhang X, Ren S, et al. Deep residual learning for image recognition[C]// Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2016: 770-778.
    
    \bibitem{lecun1998gradient}
    LeCun Y, Bottou L, Bengio Y, et al. Gradient-based learning applied to document recognition[J]. Proceedings of the IEEE, 1998, 86(11): 2278-2324.
    
    \bibitem{hinton2006fast}
    Hinton G E, Osindero S, Teh Y W. A fast learning algorithm for deep belief nets[J]. Neural Computation, 2006, 18(7): 1527-1554.
    
    \bibitem{huang2017densely}
    Huang G, Liu Z, Van Der Maaten L, et al. Densely connected convolutional networks[C]// Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2017: 4700-4708.
    
    \bibitem{howard2017mobilenets}
    Howard A G, Zhu M, Chen B, et al. Mobilenets: Efficient convolutional neural networks for mobile vision applications[J]. arXiv preprint arXiv:1704.04861, 2017.
    
    \bibitem{sandler2018mobilenetv2}
    Sandler M, Howard A, Zhu M, et al. Mobilenetv2: Inverted residuals and linear bottlenecks[C]// Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2018: 4510-4520.
    
    \bibitem{zhang2018shufflenet}
    Zhang X, Zhou X, Lin M, et al. Shufflenet: An extremely efficient convolutional neural network for mobile devices[C]// Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2018: 6848-6856.
    
    \bibitem{tan2019efficientnet}
    Tan M, Le Q V. Efficientnet: Rethinking model scaling for convolutional neural networks[C]// International Conference on Machine Learning. 2019: 6105-6114.
    
    \bibitem{hu2018squeezeandexcitation}
    Hu J, Shen L, Sun G. Squeeze-and-excitation networks[C]// Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2018: 7132-7141.
    
    \bibitem{survey2023}
    Liu Y, Sun P, Li D, et al. A survey of deep learning techniques for image recognition[J]. arXiv preprint arXiv:2303.01548, 2023.
    
    \bibitem{deng2009imagenet}
    Deng J, Dong W, Socher R, et al. Imagenet: A large-scale hierarchical image database[C]// Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2009: 248-255.
    
    \bibitem{russakovsky2015imagenet}
    Russakovsky O, Deng J, Su H, et al. Imagenet large scale visual recognition challenge[J]. International Journal of Computer Vision, 2015, 115(3): 211-252.
    
    \bibitem{krizhevsky2009learning}
    Krizhevsky A. Learning multiple layers of features from tiny images[R]. University of Toronto, 2009.
    
\end{thebibliography}
